---
title: "Hypertension Results"
author: "Rob Willans"
date: "15/03/2022"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Read in data

library(tidyverse)
library(janitor)

#Function to create factor threshold
#1 used as cutoff for missing values

create_threshold <- function(df, variable_name, new_variable_name, threshold){
  
  df %>% mutate("{{new_variable_name}}" := case_when({{ variable_name }} > threshold ~ paste0("over_", {{threshold}}),
                                              {{ variable_name }} > 1 ~ paste0("under_", {{threshold}}),
                                              TRUE ~ paste0("not_recorded")))
}

summary_table <- function(df, ...){
  
df %>% 
  group_by(...) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(percentage = n / sum(n)) %>% 
  janitor::adorn_totals()
  
}

df_input <- read_csv(
  here::here("output", "input.csv"),
  col_types = cols(patient_id = col_integer(),
                  age = col_double(),
                  last_systolic_bp_date = col_date(format = "%Y-%m-%d"),
                  last_ambulatory_systolic_bp_date = col_date(format = "%Y-%m-%d"),
                  last_ambulatory_systolic_bp_date_narrow = col_date(format = "%Y-%m-%d")
                  )
)

# Add flag for under 80
data <- df_input %>%
  create_threshold(age, age_cutoff, 80) %>% 
  create_threshold(last_systolic_bp_measure, bp_over_150_all_source, 150) %>% 
  create_threshold(last_systolic_bp_measure, bp_over_140_all_source, 140) %>% 
  create_threshold(last_systolic_bp_measure, bp_over_135_all_source, 135) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_150_broad, 150) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_150_narrow, 150) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_145_broad, 145) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_145_narrow, 145) %>%
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_140_broad, 140) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_140_narrow, 140) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_135_broad, 135) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_135_narrow, 135) 

rm(df_input)

```

## Counts (N)

### Ages

```{r agesplit}

summary_table(data, age_cutoff)

```

### All-source measurements

```{r allbp150}

summary_table(data, last_amb_bp_cutoff_140_broad)

```

```{r allbp140}

summary_table(data, bp_over_140_all_source)

```

```{r allbp135}

summary_table(data, bp_over_135_all_source)

```

### Ambulatory bps - wide def

```{r ambbp150}

summary_table(data, last_amb_bp_cutoff_150_broad)

```

```{r ambbp140}

summary_table(data, last_amb_bp_cutoff_140_broad)

```

```{r ambbp135}

summary_table(data, last_amb_bp_cutoff_135_broad)

```

### Ambulatory bps - narrow def

```{r ambbp150n}

summary_table(data, last_amb_bp_cutoff_150_narrow)

```

```{r ambbp140n}

summary_table(data, last_amb_bp_cutoff_140_narrow)

```

```{r ambbp135n}

summary_table(data, last_amb_bp_cutoff_135_narrow)

```

### Comorbidities

#### CVD

0 - No diag code 1 - Diag code

```{r cvd}

summary_table(data, CVD_code)

```

#### CKD

0 - No diag code 1 - diag code

```{r ckd}

summary_table(data, CKD_code)

```

#### T1D

0 - No diag code 1 - Diag code

```{r t1d}

summary_table(data, T1D_code)

```

#### T2D

0 - No diag code 1 - Diag code

```{r t2d}

summary_table(data, T2D_code)

```

## Adults \<80 all source BPM measure 140 systolic or less

• How many adults with hypertension aged under 80 with a diagnosis of hypertension have a clinic blood pressure below 140/90 mmHg measured in the preceding 12 months

```{r under80allsource140}

data %>% 
  filter(age < 80) %>%
  summary_table(bp_over_140_all_source)

```

## Adults \<80 home and ambulatory BPM measure 135 systolic or less

• How many adults with hypertension aged under 80 with a diagnosis of hypertension have a blood pressure measured using ABPM or HBPM below 135/85 mmHg in the preceding 12 months?

### Broad defn

```{r under80ambsource135broad}

data %>% 
  filter(age < 80) %>% 
  summary_table(last_amb_bp_cutoff_135_broad)

```

### Narrow defn

```{r under80ambsource135narrow}

data %>% 
  filter(age < 80) %>% 
  summary_table(last_amb_bp_cutoff_135_narrow)

```

## Overlap 140 all source and 135 ambulatory (under 80)

```{r overlapclinicamb}

data %>% 
  filter(age < 80) %>% 
  summary_table(bp_over_140_all_source, last_amb_bp_cutoff_135_broad)

```

## Count of number of patients where age<80 and bp is under 140 (all source) but over 135 (ambulatory)

```{r overlap2}

data %>% 
  filter(age < 80,
         bp_over_140_all_source == 'under_140',
         last_amb_bp_cutoff_135_broad == 'over_135') %>% 
  summary_table(bp_over_140_all_source, last_amb_bp_cutoff_135_broad)

```


## Adults \> 80

• How many adults with hypertension aged 80 and over with a diagnosis of hypertension have a clinic blood pressure below 150/90 mmHg measured in the preceding 12 months.

```{r over80all}

data %>% 
  filter(age >= 80) %>% 
  summary_table( bp_over_150_all_source)

```

• How many adults with hypertension aged 80 and over with a diagnosis of hypertension have a blood pressure measured using ABPM or HBPM below 145/85 mmHg measured in the preceding 12 months.

```{r over80ambwide}

data %>% 
  filter(age >= 80) %>% 
  summary_table(last_amb_bp_cutoff_145_broad)
```

```{r over80ambnarrow}

data %>% 
  filter(age >= 80) %>% 
  summary_table(last_amb_bp_cutoff_145_narrow)

```

## Overlap 150 all source and 145 ambulatory (over 80)

```{r overlapclinicamb}

data %>% 
  filter(age >= 80) %>% 
  summary_table(bp_over_150_all_source, last_amb_bp_cutoff_145_broad)

```

## Count of number of patients where age 80+ and bp is under 150 (all source) but over 135 (ambulatory)

```{r overlap2ober80}

data %>% 
  filter(age >= 80,
         bp_over_150_all_source == 'under_150',
         last_amb_bp_cutoff_145_broad == 'over_145') %>% 
  summary_table(bp_over_150_all_source, last_amb_bp_cutoff_145_broad)

```
