---
title: "Hypertension Results"
author: "Rob Willans"
date: "15/03/2022"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Read in data

library(tidyverse)
library(janitor)

#Function to create factor threshold
#1 used as cutoff for missing values

create_threshold <- function(df, variable_name, new_variable_name, threshold){
  
  df %>% mutate("{{new_variable_name}}" := case_when({{ variable_name }} > threshold ~ paste0("over_", {{threshold}}),
                                              {{ variable_name }} > 1 ~ paste0("under_", {{threshold}}),
                                              TRUE ~ paste0("not_recorded")))
}

df_input <- read_csv(
  here::here("output", "input.csv"),
  col_types = cols(patient_id = col_integer(),
                  age = col_double(),
                  last_systolic_bp_date = col_date(format = "%Y-%m-%d"),
                  last_ambulatory_systolic_bp_date = col_date(format = "%Y-%m-%d"),
                  last_ambulatory_systolic_bp_date_narrow = col_date(format = "%Y-%m-%d")
                  )
)

# Add flag for under 80
data <- df_input %>%
  create_threshold(age, age_cutoff, 80) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_140_broad, 140) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_140_narrow, 140) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_135_broad, 135) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_135_narrow, 135) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_145_broad, 145) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_145_narrow, 145) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure, last_amb_bp_cutoff_150_broad, 150) %>% 
  create_threshold(last_ambulatory_systolic_bp_measure_narrow, last_amb_bp_cutoff_150_narrow, 150)
  
  
```

## Under age 80

### Proportion of data with last ambulatory systolic bp measurement above 140

#### Broad coding definition

```{r freqtabsforbps140broad}

data %>% 
  filter(age < 80) %>% 
  tabyl(last_amb_bp_cutoff_140_broad)

```

#### Narrow coding definition

```{r freqtabsforbps140narrow}

data %>% 
  filter(age < 80) %>% 
  tabyl(last_amb_bp_cutoff_140_narrow)

```

### Proportion of data with last ambulatory systolic bp measurement above 135

#### Broad coding definition

```{r freqtabsforbps135broad}

data %>% 
  filter(age < 80) %>% 
  tabyl(last_amb_bp_cutoff_135_broad)

```

#### Narrow coding definition

```{r freqtabsforbps135narrow}

data %>% 
  filter(age < 80) %>% 
  tabyl(last_amb_bp_cutoff_135_narrow)

```

### Frequency Table - narrow bp coding, 140 and 135 thresholds

#### Broad coding defintition

```{r freqtabsforbpsbroad135and140}

data %>% 
  filter(age < 80) %>% 
  group_by(last_amb_bp_cutoff_135_broad, last_amb_bp_cutoff_140_broad) %>% 
  summarise(n = n(), .groups = "keep")

```

#### Narrow coding defintion

```{r freqtabsforbpsnarrow135and140}

data %>% 
  filter(age < 80) %>% 
  group_by(last_amb_bp_cutoff_135_narrow, last_amb_bp_cutoff_140_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```

### Stratified by CVD, CKD, and DM - last ambulatory sbp over 140

Broad coding definition only

#### CKD

0 - No CKD diag code
1 - CKD diag code

```{r bp140broadvsCKD}

data %>% 
  filter(age < 80) %>% 
  group_by(last_amb_bp_cutoff_140_broad, CKD_code) %>% 
  summarise(n = n(), .groups = "keep")

```

#### CVD

0 - No CVD diag code
1 - CvD diag code

```{r bp140broadvsCVD}

data %>% 
  filter(age < 80) %>% 
  group_by(last_amb_bp_cutoff_140_broad, CVD_code) %>% 
  summarise(n = n(), .groups = "keep")

```

#### T1D

0 - No T1D diag code
1 - T1D diag code


```{r bp140broadvsT1D}

data %>% 
  filter(age < 80) %>% 
  group_by(last_amb_bp_cutoff_140_broad, T1D_code) %>% 
  summarise(n = n(), .groups = "keep")

```

#### T2D

0 - No T2D diag code
1 - T2D diag code

```{r bp140broadvsT2D}

data %>% 
  filter(age < 80) %>% 
  group_by(last_amb_bp_cutoff_140_broad, T2D_code) %>% 
  summarise(n = n(), .groups = "keep")

```

### SBP between 140 and 135

#### CKD

All narrow coding definition

```{r bp140and135narrowCKD}

data %>% 
  filter(age < 80,
         CKD_code == 1) %>% 
  group_by(last_amb_bp_cutoff_140_narrow, last_amb_bp_cutoff_135_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```

#### CVD

```{r bp140and135narrowCVD}

data %>% 
  filter(age < 80,
         CVD_code == 1) %>% 
  group_by(last_amb_bp_cutoff_140_narrow, last_amb_bp_cutoff_135_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```

#### T1D

```{r bp140and135narrowT1D}

data %>% 
  filter(age < 80,
         T1D_code == 1) %>% 
  group_by(last_amb_bp_cutoff_140_narrow, last_amb_bp_cutoff_135_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```

#### T2D

```{r bp140and135narrowT2D}

data %>% 
  filter(age < 80,
         T2D_code == 1) %>% 
  group_by(last_amb_bp_cutoff_140_narrow, last_amb_bp_cutoff_135_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```

## 80 and above

### SBP between 150 and 145 

#### Broad coding defintion

```{r SBPbetween150and14580plusbroad}

data %>% 
  filter(age >= 80) %>% 
  group_by(last_amb_bp_cutoff_150_broad, last_amb_bp_cutoff_145_broad) %>% 
  summarise(n = n(), .groups = "keep")

```


#### Narrow coding definition

```{r SBPbetween150and14580plusnarrow}

data %>% 
  filter(age >= 80) %>% 
  group_by(last_amb_bp_cutoff_150_narrow, last_amb_bp_cutoff_145_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```


### SBP over 150 BP atratified by CVD, CKD and DM 

#### Broad coding definition

##### CKD

0 - No CKD diag code
1 - CKD diag code

```{r bp140broadvsCKDover80}

data %>% 
  filter(age >= 80) %>% 
  group_by(last_amb_bp_cutoff_150_broad, CKD_code) %>% 
  summarise(n = n(), .groups = "keep")

```

##### CVD

0 - No CVD diag code
1 - CvD diag code

```{r bp140broadvsCVDover80}

data %>% 
  filter(age >= 80) %>% 
  group_by(last_amb_bp_cutoff_150_broad, CVD_code) %>% 
  summarise(n = n(), .groups = "keep")

```

##### T1D

0 - No T1D diag code
1 - T1D diag code


```{r bp140broadvsT1Dover80}

data %>% 
  filter(age >= 80) %>% 
  group_by(last_amb_bp_cutoff_150_broad, T1D_code) %>% 
  summarise(n = n(), .groups = "keep")

```

##### T2D

0 - No T2D diag code
1 - T2D diag code

```{r bp140broadvsT2Dover80}

data %>% 
  filter(age >= 80) %>% 
  group_by(last_amb_bp_cutoff_150_broad, T2D_code) %>% 
  summarise(n = n(), .groups = "keep")

```

### SBP between 150 and 145 

#### Narrow coding definition

##### CKD

```{r bp150and145narrowCKDover80}

data %>% 
  filter(age >= 80,
         CKD_code == 1) %>% 
  group_by(last_amb_bp_cutoff_150_narrow, last_amb_bp_cutoff_145_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```

##### CVD only

```{r bp150and145narrowCVDover80}

data %>% 
  filter(age >= 80,
         CVD_code == 1) %>% 
  group_by(last_amb_bp_cutoff_150_narrow, last_amb_bp_cutoff_145_narrow) %>% 
  summarise(n = n(), .groups = "keep")


```

##### T1D only

```{r bp150and145narrowT1dDover80}

data %>% 
  filter(age >= 80,
         T1D_code == 1) %>% 
  group_by(last_amb_bp_cutoff_150_narrow, last_amb_bp_cutoff_145_narrow) %>% 
  summarise(n = n(), .groups = "keep")

```

##### T2D only

```{r bp150and145narrowT2dDover80}

data %>% 
  filter(age >= 80,
         T1D_code == 1) %>% 
  group_by(last_amb_bp_cutoff_150_narrow, last_amb_bp_cutoff_145_narrow) %>% 
  summarise(n = n(), .groups = "keep")
